quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-19 paper-quollr.tex
Updated hex_param_vis configurations

\begin{figure}
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/fig-hex-param-1} \caption{The components of the hexagon grid illustrating notation.}\label{fig:fig-hex-param}
\end{figure}

>>>>

\begin{figure}[H]

{\centering \includegraphics[width=0.5\linewidth]{paper-quollr_files/figure-latex/hex-param-1}

}

\caption{The components of the hexagon grid illustrating notation.}\label{fig:hex-param}
\end{figure}
